Reproducing anaylses of Beninca et al (2008)

### 2016-04-04 code/report.Rmd
figure 2, 3, 4 fixed (hopefully)

The graph with abundances fourth root transformed, as this is the transformation used in analyses in the original publication.
```{r, warning=FALSE, fig.width=10}
g1 <- ggplot(aes(x=as.numeric(Day.number), y=value^0.25, col=variable), data=all.data) +
  xlab("Time (days)") + ylab("Abundance value ^ 0.25") +
  facet_wrap(~Type, ncol=2, scales="free_y") +
  geom_line() +
  scale_colour_manual(values = species.colour.mapping)
g1
```

@@

## graph
ggplot(two.datasets, aes(x=Abundance, y=stand.y)) + geom_point() +
  facet_wrap(~variable) +
  geom_abline(slope=1, intercept = 0, colour="red") +
  xlab("Values from published data") +
  ylab("Reproduced values")

@@

Cosmetic work on the table:
```{r}
oo <- c(10, 9, 8, 11, 12, 6, 5, 3, 4, 2)
cor.coefs1 <- cor.coefs[oo,oo]
cor.cp1 <- cor.cp[oo,oo]
for(i in 1:length(cor.cp1[1,]))
  for(j in 1:i)
  cor.cp1[i,j] <- ""
sn <- substr(rownames(cor.cp1), 1, 4)
sn[4:5] <- c("N", "P")
dimnames(cor.cp1) <- list(sn, sn)
```

@@

qplot(x=as.vector(original.cors), y=as.vector(cor.coefs1), ylim = c(-0.4,0.4), xlim=c(-0.4, 0.4),
      xlab="Correlations in original article", ylab="Correlations calculated\nin this reproduction") + geom_abline(intercept=0,slope=1, colour="red")
```

@@

Do the time-delayed embedding, and save the data for the graphs:
```{r, message=FALSE, error=TRUE}
all.species <- unique(as.character(led$variable))
diverg <- matrix(NA, time.steps, length(all.species))
colnames(diverg) <- all.species
for(i in 1:length(all.species)) {
  print(all.species[i])
  tr.fs <- filter(final, variable==all.species[i])$y
  diverg[,i] <- as.numeric(try(lyap_k(tr.fs,
                                      m=embedding.dimension,
                                      d=time.delay,
                                      k=10, # number of considered neighbours 20
                                      ref=40, # number of points to take into account 100
                                      t=Theiler.window,
                                      s=time.steps,
                                      eps=10 # radius where to find nearest neighbours 10
                                      )))
}
## a bit of a fudge with the translation to days
diverg <- as.data.frame(cbind(days=1:time.steps, diverg))
diverg <- gather(diverg, Species, Difference, 2:10, convert=F)
diverg$days <- diverg$days*3.35
```

@@

## ensure order of panels in figure same as in original
diverg$Species_short <- factor(diverg$Species_short,
                               levels=c("Calanoid.copepods", "Rotifers",
                                        "Nanophytoplankton", "Picophytoplankton",
                                        "Ostracods", "Harpacticoids", "Bacteria",
                                        "N","P"))

g1 <- ggplot(diverg, aes(x=days, y=Difference)) + geom_point() + facet_wrap(~Species_short) +
  geom_text(data=LEs, aes(x=60, y=0, label=round(le,3)))
g1
```

>>>>

The graph with abundances fourth root transformed, as this is the transformation used in analyses in the original publication.
```{r, warning=FALSE, fig.width=10}

##########################
## Figure 1 in the article
g1 <- ggplot(aes(x=as.numeric(Day.number), y=value^0.25, col=variable), data=all.data) +
  xlab("Time (days)") + ylab("Abundance value ^ 0.25") +
  facet_wrap(~Type, ncol=2, scales="free_y") +
  geom_line() +
  scale_colour_manual(values = species.colour.mapping)
g1
```

@@

##########################
## Figure 2 in the article
ggplot(two.datasets, aes(x=Abundance, y=stand.y)) + geom_point() +
  facet_wrap(~variable) +
  geom_abline(slope=1, intercept = 0, colour="red") +
  xlab("Values from published data") +
  ylab("Reproduced values")

@@

Cosmetic work on the table:
```{r}
oo <- c("Bacteria", "Harpacticoids", "Ostracods",
        "Total.dissolved.inorganic.nitrogen", "Soluble.reactive.phosphorus",
        "Picophytoplankton", "Nanophytoplankton", "Rotifers",
        "Protozoa", "Calanoid.copepods")
cor.coefs1 <- cor.coefs[oo,oo]
cor.cp1 <- cor.cp[oo,oo]
for(i in 1:length(cor.cp1[1,]))
  for(j in 1:i)
  cor.cp1[i,j] <- ""
sn <- substr(rownames(cor.cp1), 1, 4)
sn[4:5] <- c("N", "P")
dimnames(cor.cp1) <- list(sn, sn)
```

@@

##########################
## Figure 3 in the article
qplot(x=as.vector(original.cors), y=as.vector(cor.coefs1), ylim = c(-0.4,0.4), xlim=c(-0.4, 0.4),
      xlab="Correlations in original article", ylab="Correlations calculated\nin this reproduction") + geom_abline(intercept=0,slope=1, colour="red")
```

@@

Do the time-delayed embedding, and save the data for the graphs:
```{r, message=FALSE, error=TRUE}
all.species <- unique(as.character(led$variable))
diverg <- matrix(NA, time.steps, length(all.species))
colnames(diverg) <- all.species
for(i in 1:length(all.species)) {
  print(all.species[i])
  tr.fs <- filter(final, variable==all.species[i])$y
  diverg[,i] <- as.numeric(try(lyap_k(tr.fs,
                                      m=embedding.dimension,
                                      d=time.delay,
                                      k=10, # number of considered neighbours 20
                                      ref=40, # number of points to take into account 100
                                      t=Theiler.window,
                                      s=time.steps,
                                      eps=10 # radius where to find nearest neighbours 10
                                      )))
}
## a bit of a fudge with the translation to days
diverg <- as.data.frame(cbind(days=1:time.steps, diverg))
diverg <- gather(diverg, Species, Difference, 2:10, convert=F)
diverg$Species <- as.factor(diverg$Species)
diverg$days <- diverg$days*3.35
```

@@

## ensure order of panels in figure same as in original
## This does affect panel order on Owen's computer
diverg$Species_short <- factor(diverg$Species_short,
                               levels=c("Calanoid.copepods", "Rotifers",
                                        "Nanophytoplankton", "Picophytoplankton",
                                        "Ostracods", "Harpacticoids", "Bacteria",
                                        "N","P"))

## This puts the panels in alphabetical order if uncommented
#diverg$Species_short <- factor(diverg$Species_short,
#                               levels=sort(c("Calanoid.copepods", "Rotifers",
#                                        "Nanophytoplankton", "Picophytoplankton",
#                                        "Ostracods", "Harpacticoids", "Bacteria",
#                                        "N","P")))

str(LEs)
levels(LEs$Species_short)

##########################
## Figure 4 in the article
g1 <- ggplot(diverg, aes(x=days, y=Difference)) + geom_point() + facet_wrap(~Species_short) +
  geom_text(data=LEs, aes(x=60, y=0, label=round(le,3)))
g1
```
